---
title: "Viz_and_Eda"
author: "Arielle"
date: "9/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tidyverse)
library (ggridges)
```

## R Markdown

```{r load data,}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

## create a ggplot
```{r}
ggplot(weather_df, aes(x= tmin, y = tmax))
```
##only defined two out of the three things, only told the min and max but didnt add the geomeotry

```{r}
ggplot(weather_df, aes(x= tmin, y = tmax)) + geom_point()
```

##Alternative way of making plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point()
```
```{r}
scatterplot= 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

scatterplot
```
### Adding color

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color=name))

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color=name), alpha = 0.4)
```
## why do positions matter?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color=name), alpha = 0.4) +
  geom_smooth(se = FALSE)

ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .4) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```
##color matters in geom_pont but not geom_smoothb

## this is fine but not interesting 

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color= name)) +
  geom_point() +
  geom_smooth(se= FALSE)

weather_df %>% 
  ggplot(aes(x = date, y = prcp, color= name)) +
  geom_point() +
  geom_smooth(se= FALSE)

weather_df %>% 
  ggplot(aes(x = date, y = tmax, color= name)) +
  geom_point(aes(size = prcp), alpha = 0.5) +
  geom_smooth( size = 2, se= FALSE)
```

## Some extra stuff
## You dont have to have all the geometry can choose what you want 
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color= name)) +
  geom_smooth( size = 2, se= FALSE)
```

##install package
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color= name)) +
  geom_bin2d() 
  
```

##more kinds of plots

```{r}
weather_df %>% 
  ggplot(aes(x= tmax, fill= name)) + 
  geom_histogram()

weather_df %>% 
  ggplot(aes(x= tmax, fill= name)) + 
  geom_histogram(position= "dodge")

weather_df %>% 
  ggplot(aes(x= tmax, fill= name)) + 
  geom_histogram() +
  facet_grid(~name)

weather_df %>% 
  ggplot(aes(x= tmax, fill= name)) + 
  geom_density(alpha= 0.3)
```

## Other Univariate things 

```{r}
weather_df %>% 
  ggplot(aes(x= name, y= tmax)) +
  geom_boxplot()

weather_df %>% 
  ggplot(aes(x= name, y= tmax)) +
  geom_violin()
```

##Ridge Plot
```{r}
weather_df %>% 
  ggplot(aes(x= tmax, y= name)) +
  geom_density_ridges()
```

